---
title: "Dictionary"
author: "Annie"
date: "February 23, 2019"
output: html_document
---

#Dictionary

##General bits
1. help(topic)

2. ?topic

3. ls()

4. dir()

5. list.files()

##Input and output
1. save()

2. load()

3. data()
This function allows you to search for pre-made data sets in r
ex.
```{r}
?data
data()
```

4. library()
This code allows you to access a package and insert it into your code. Then it allows your package to work for the code chunk.
ex.
```{r}
library(ggplot2)
Names <- rep(c("Dara", "Azalea", "Barbi", "Rowena", "Fiona"),each=2)
MF <- rnorm(10, 45, 25)
Condition <- rep(c("Social", "Nonsocial"), 5)
Aversity <- rep(c("A", "N_A"), times=c(4,6))
plot_df <- data.frame (Names, MF, Condition, Aversity)

ggplot(plot_df, aes(x=Condition, y=MF, group=Names, 
                    linetype=Aversity))

```

5. read.table()

6. read.csv()

7. scan()

8. print()
This function analyzes the results of your code (executing all the commands)
ex.
```{r}
data.frame(1,2,3,4)
print(data.frame())
```

9. cat()

10. write.table()

##Data Creation
1. c()
This function is used to combine elements (factors in a vectore for example)


2. from:to (where from and to are replaced with numbers, e.g. 1:10)

3. seq()

4. rep()

5. data.frame()
This allows one to enter specific groups of data values
ex.
```{r}
data.frame(1, 2, 3, 5)
```

6. list()

7. matrix()

8. factor()

9. rbind()

10. cbind()

##Slicing and extracting data indexing vectors
x[n] nth element
x[-n] all but nth element
x[1:n] first n elements
x[-(1:n)] elements from n+1 to the end
x[c(1,4,2)] specific elements
x[“name”] elements named “name”
x[x>3] all elements greater than 3
x[x > 3 & x < 5] all elements between 3 and 5
x[x %in% c(“a”,“and”,“the”)] all elements in given set

##Indexing lists
x[n] list with elements n
x[[n]] nt h element of the list
x[[“name”]] element of the list named “name”
x$name id.

##Indexing matrices
x[i,j] element at row i, column j
x[i,] row i
x[,j] column j
x[,c(1,3)] columns 1 and 3
x[“name”,] row named “name”
Indexing data frames (matrix indexing plus the following)
x[[“name”]] column named “name”
x$nameid.

##Variable conversion
as.data.frame(x)
as.numeric(x)
as.logical(x)
as.character(x)

##Variable information
is.na(x)
is.null(x)
is.data.frame(x)
is.numeric(x)
is.character(x)
length(x)
dim(x)
dimnames(x)
nrow(x)
ncol(x)
class()
attributes()

##Data selection and manipulation
which.max()
which.min()
which()
sort()
unique()
table()
sample()

##Math
max()
This sets the maximum value included in a data set (and graph)

min()
This set the minimum value included in a data set (and graph)

range()
This determines the range of numbers considered in a graph

sum()
This function adds all the numbers in a given set

mean()
Creates the mean of a given set of number values

median()
calculates the median of a set of numbers

var()
sd()
cor()
round()
abs()

##Matrices
t()
diag()
rowSums()
colSums()
rowMeans()
colMeans()

##Advanced Data processing
apply()
aggregate()
Strings
paste()
strsplit()
tolower()
toupper

##Plotting
hist()
This function creates a histogram graph of a given set of data

plot()
This function creates a plot graph of a given set of data

##Distributions
rnorm()
This function inserts a normal distribution

runif()

##Programming
show that you can define a function
show that you can write a for loop
show that you can write a while loop
show that you can write an if else statement
Explain what return() does inside a function, show you can use it
Explain what break() does, show you can use it

##Installing some packages
Use the packages tab in R-studio to install these packages. You will need to be connected to the internet when you do this. If you are installing on your laptop, or on R-studio Cloud, then these packages will not need to installed again.

ggplot2
dplyr
shiny
data.table
reshape2
stringr
