---
title: "More Practice"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# Practice Problems

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}
x<-c(1:100)
for (i in 1:100) {
  print (i)
  
}

```


Find the sum of all the integer numbers from 1 to 100

```{r}
sum(seq(1,100))
```

List all of the odd numbers from 1 to 100

```{r}
a<-length(1:99)
for (i in 1:99){
  if(!i %%2){
    next
  }
  print(i)
}

```

List all of the prime numbers from 1 to 1000


Generate 100 random numbers
```{r}
a<-(1:100)
runif(a, min=1, max=100)
```

Generate 100 random numbers within a specific range

```{r}
a<-(1:100)
runif(a, min=1, max=500)
```

Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation

